Product graphics

### 2009-05-13 product-graphics.tex
Update data, add description to paper

>>>>

To illustrate the techniques in this paper, we'll use a small sample from the general social survey ({\sc gss}) focussing on happiness.  51\,020 observations from a yearly survey from 1972 to 2006.  Happy, age, sex, marital status, terminal education level, relative financial status and health.  Also contains a weighting variable wtssall, which is a probability weight from the survey.

The survey also contains a respondent id variable.  4510 people in sample,  1271 people interviewed only once, 1107 interviewed every year.
